### 2016-09-30 notions.tex
fixing linebreaks and other cleaning

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
any attacker $A$, there is an attacker
$A'$ running in about the same time for which
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform values $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
and returns $\pubaux
\getsr \Rep_2(|S|, y_1, \ldots, y_t)$.

@@

Now, consider an experiment $G1$ in which computation is done as follows:
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $A(\pubaux)$.
\end{enumerate}
It is immediate that the difference between the probability that $A$ outputs~1 in
$G1$ and the probability that it outputs~1 in
$G0$ is bounded by $\AdvPRF{F}{A'}$, where $A'$ performs the
obvious simulation.

>>>>

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
any attacker $A$, there is an attacker
$B$ running in about the same time for which
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform values $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
and returns $\pubaux
\getsr \Rep_2(|S|, y_1, \ldots, y_t)$.

@@

Now, consider an experiment $G1$ in which computation is done as follows:
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $A(\pubaux)$.
\end{enumerate}
It is immediate that the difference between the probability that $A$ outputs~1 in
$G1$ and the probability that it outputs~1 in
$G0$ is bounded by $\AdvPRF{F}{B}$, where $B$ performs the
obvious simulation.

### 2016-09-30 results.tex
fixing linebreaks and other cleaning

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
%\input{Theorem3_FP}

@@

\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}
\todo{Typeset simple proof.  Result is on chalkboard.}

@@

\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
\end{theorem}

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as
input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random
function~$\rho$ itself.  However, it has no information about the
bit~$z$, so at best it can cause~$A$ to output 1 with
probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$.
\end{proof}

@@

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be laughable in many applications, and a
$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
that, as described in~\cite{xxx}, $\lambda$ must be at least the
bitlength of the longest element $x \in S$. \tsnote{This could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid\cite{squid}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a
commodity laptop.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.

@@

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of GBF with secret hash functions}]
\label{thm:gbf-prf-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.  It returns~$M$ as $\pubaux$.
\end{proof}

>>>>

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
\todo{move proof back in-line.}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
%\input{Theorem3_FP}

@@

\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}\;.
\]
\end{theorem}
\todo{Typeset simple proof.  Result is on chalkboard.}

@@

\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
\end{theorem}
\todo{some form of proof ---at least a proof sketch in the text--- needs to appear here!}

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$. \hfill\qed
\end{proof}

@@

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,\linebreak s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.  It returns~$M$ as $\pubaux$. \hfill\qed
\end{proof}

@@

On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as
input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random
function~$\rho$ itself.  However, it has no information about the
bit~$z$, so at best it can cause~$A$ to output 1 with
probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
\end{proof}

@@

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be prohibitive in many applications, and a
$2^{-80}$ false-postive rate would be typically considered overkill in
practice.\footnote{Note
that, as described in~\cite{xxx}, $\lambda$ must be at least the
bitlength of the longest element $x \in S$. \tsnote{This could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid\cite{squid}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a
commodity laptop.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.

@@

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of GBF with secret hash functions}]
\label{thm:gbf-prf-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.  It returns~$M$ as $\pubaux$.\hfill\qed
\end{proof}
